Tree size, microhabitat, and hydraulic traits (interactively) shape drought response in a temperate broadleaf forest

### 2019-08-02 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd
finished (for now) with hypotheses/ predictions.

2.1. Commonly measured traits including wood density (REFS), leaf mass per area [@abrams_adaptations_1990] [@guerfel_impacts_2009], and ring porosity (Elliot et al. 2015, Friedrichs et al. 2009) have been linked to drought responses and likely correlated with drought resistance in this forest. However, we hypothesize that leaf hydraulic traits such as leaf area shrinkage upon dessication and turgor loss point, which are emerging as potentially more informative traits but whose effect on drought resistance has never been tested (CONFIRM), will prove better predictors.
    * P2.1 - wood density correlates positively drought resistant
    * P2.2 - leaf mass area correlates positively to drought resistance 
    * P2.3 - diffuse porous species are more sensitive than ring porous  
    * P2.4 -leaf area shrinkage upon dessication (PLA) is negatively correlated with drought resistance
    * P2.5 - TLP correlates negatively with drought resistance

@@

[differences among droughts:]
**I think for #4 here the focus should be on hypotheses looking at the overall trend compared to the specific scenarios?**

**1. How significant are individual drought years on a long time-frame trend?**
1.1 Individual drought scenario is a strong predictor of drought stress.

    * P1.1 - Drought stress is proportional to the severity of each drought.

**4. How do droughts vary in their effect on tree resistance? **

    * P4.1 - The combined-years scenario will have more explaining variables than the individual scenarios.
    * P4.2 - Inclusion of leaf hydraulic traits does not eliminate or significantly reduce effect of tree size.
    * P4.3 - Drought resistance for each scenario will be explained more by hydraulic traits than by the biophysical environment

>>>>

2.1. Commonly measured traits including wood density (REFS), leaf mass per area [@abrams_adaptations_1990] [@guerfel_impacts_2009], and ring porosity (Elliot et al. 2015, Friedrichs et al. 2009) have been linked to drought responses and likely correlated with drought resistance in this forest. However, we hypothesize that leaf hydraulic traits such as leaf area shrinkage upon dessication and turgor loss point, which are emerging as potentially more informative traits but whose effect on drought resistance has never been tested (CONFIRM), will prove better predictors.
    * P2.1 - wood density correlates positively drought resistant
    * P2.2 - leaf mass area correlates positively to drought resistance 
    * P2.3 - diffuse porous species are more sensitive than ring porous  
    * P2.4 -leaf area shrinkage upon dessication (PLA) is negatively correlated with drought resistance (supported as one of the best predictors)
    * P2.5 - TLP correlates negatively with drought resistance  (supported as one of the best predictors)

@@

**3. Did responses vary across droughts?**
3.1 Overall community response is proportional to the severity of each drought.

    * P3.1 -  (How do you define severity? min PDSI? duration? it may be tricky to find the right metric, but I agree that its interesting to compare across droughts)

3.2. Predictor variables varied across droughts.

    * P3.2 - There will be overall consistnecy in terms of the directions of responses to predictor variables; however, the best set of predictor variables will vary across droughts.
